KeysarMouseTracking.csv

### 2016-05-12 experiment2/analysis/exp2Analysis.Rmd
Merged stashed changes

setwd('~/Repos/keysar_replication/experiment2/data/')
preMouseDExp2 = read.csv('mouse/exp2Mouse.csv')
preErrorDExp2 = read.csv('error/exp2Error.csv')
preMessageDExp2 = read.csv('message/exp2Message.csv')
library(tidyr)
library(dplyr)
library(ggplot2)
library(lme4)
library(lmerTest)
```

@@

```{r}
itemInequalitiesExp2 <- errorDExp2 %>%
  filter(condition == "exp") %>%
  filter(criticalError == 1) %>%
  filter(attemptNum == 0) %>%
  group_by(objectSet) %>%
  tally() %>%
  right_join(numPlayersPerConditionExp2, by = c('objectSet')) %>%
  mutate(objectSet = objectSet,
         errorCount = n, 
         correctCount = total - n) %>%
  mutate(errorRate = errorCount / (errorCount + correctCount)) %>%
  select(objectSet, errorCount, correctCount, errorRate, total)

@@

```{r}
library(binom)
Exp1Errs = itemInequalitiesExp1 %>%
  mutate(response = errorRate) %>%
  mutate(measure = "error") %>%
  do(mutate(., lower = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$lower,
               upper = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$upper)) %>%
  select(objectSet, response, condition, lower, upper)

@@

Exp1ItemwiseForPlot = rbind(Exp1PlottingDF, Exp1Errs)
g <- (ggplot(Exp1ItemwiseForPlot, aes(x = objectSet, y = response, 
                                      group = measure, fill = measure))
  + geom_bar(stat = "identity", position = "dodge")
  + geom_errorbar(aes(ymax = upper, ymin = lower), 
                  position = dodge, width = 0.25)
  + theme_bw(base_size = 16) 
  + ggtitle("Exp.1 Item-Wise Error")
  + ylab("ratio (scaled)"))
g
ggsave("../../writing/cogsci-submission/images/itemWiseFitness.pdf")
```

@@

```{r}
mouDataExp2 <- mouseDExp2 %>%
  filter(attemptNum == 0)

@@

joinedExp2 <- mouDataExp2 %>%
  right_join(mDExp2, by = c("gameid", "condition", "objectSet", "instructionNum",
                            "attemptNum", "critical")) #%>%
#   left_join(errorDExp2, by = c("gameid", "condition", "objectSet", "attemptNum",
#                                "instructionNum", "critical"))
```

```{r}
dExp2 <- joinedExp2 %>% 
  filter(critical == 1) %>% 
  group_by(objectSet, condition) %>%
  filter(time > messageStamp) %>%
  mutate(mouseY = 600 - mouseY) %>%
  mutate(targetY = 600 - targetY) %>%
  mutate(begTargetX = first(targetX),
         begTargetY = first(targetY),
         distractorX = as.numeric(levels(distractorX))[distractorX],
         distractorY = 600 - as.numeric(levels(distractorY))[distractorY]) %>%
   mutate(begDistrX = first(distractorX),
          begDistrY = first(distractorY)) %>%
   filter(targetX == begTargetX) %>%
   filter(targetY == begTargetY) %>%
   filter(distractorX == begDistrX) %>%
   filter(distractorY == begDistrY) 
```

@@

heatMapForLMExp2 <- dExp2 %>%
  group_by(gameid, objectSet) %>%
  mutate(inTargetSquare = as.numeric(mouseX > targetX - 75 
                                     & mouseX < targetX + 75
                                     & mouseY > targetY - 75
                                    & mouseY < targetY + 75)) %>%
  mutate(inDistractorSquare = as.numeric(mouseX > distractorX - 75
                                         & mouseX < distractorX + 75
                                         & mouseY > distractorY - 75
                                         & mouseY < distractorY + 75)) %>%
  group_by(gameid, condition) %>%
  summarise(distractor = sum(inDistractorSquare) / n(),
         target = sum(inTargetSquare) / n()) %>%
  gather(cellType, percent, distractor, target)

heatMapForLMExp2

t1 <- lm(percent ~ condition , data = heatMapForLMExp2 %>% filter(cellType == "target"))
summary(t1)
```

@@

```{r}
heatMapForPlotExp2 <- dExp2 %>%
  group_by(gameid, objectSet) %>%
  mutate(inTargetSquare = as.numeric(mouseX > targetX - 75 
                                     & mouseX < targetX + 75
                                     & mouseY > targetY - 75
                                    & mouseY < targetY + 75)) %>%
  mutate(inDistractorSquare = as.numeric(mouseX > distractorX - 75
                                         & mouseX < distractorX + 75
                                         & mouseY > distractorY - 75
                                         & mouseY < distractorY + 75)) %>%
  group_by(gameid, condition) %>%
  summarize(distractor = sum(inDistractorSquare) / n(),
            target = sum(inTargetSquare) / n()) %>%
  gather(cellType, percent, distractor, target) %>%
  group_by(condition, cellType) %>%
  summarize(error = sem(percent),
            percent = mean(percent))

heatMapForPlotExp2

g <- (ggplot(heatMapForPlotExp2, aes(x = condition, y = percent, 
                                     group = cellType, color = cellType)) 
      + geom_line(aes(linetype = cellType), size = 2)
      + geom_errorbar(aes(ymax = percent + error, 
                          ymin = percent - error), size =2 ,
                      width = 0.1)
     + ylim(0, .45)
     + theme_bw(base_size = 16)
      + ggtitle("Experiment 2 Hover-Time"))
g
ggsave("../../writing/cogsci-submission/images/exp2MouseTracking.pdf")
```

Compare mouse data from Exp1 w/ mouse data from Exp2:

```{r}
combinedHeatMap = rbind(heatMapForLMExp1 %>%
                          mutate(exp = "Exp.1") %>% 
                          filter(cellType == "target"),
                        heatMapForLMExp2 %>% 
                          mutate(exp = "Exp.2") %>%
                          filter(cellType == "target"))
combinedHeatMapForPlot <- combinedHeatMap %>%
  group_by(condition, exp) %>%
  summarize(error = ci95(percent),
            percent = mean(percent))

g <- (ggplot(combinedHeatMapForPlot, aes(x = exp, y = percent, 
                                  group = condition, fill = condition)) 
      + geom_bar(position = dodge, stat= "identity")
      + geom_errorbar(aes(ymax = percent + error, 
                          ymin = percent - error), position = dodge,
                          width = 0.25)
      + ylim(0, .5)
      + theme_bw(base_size = 16)
      + ggtitle("Target Hover-Time"))
g
ggsave("../../writing/cogsci-submission/images/mousetracking.pdf")

combinedRes = lm(percent ~ exp * condition, data = combinedHeatMap)
summary(combinedRes)
```

```{r}
# heatMapForPlot$new_labels = as.factor(sapply(X = heatMapForPlot$objectSet, 
#                               FUN = function(v) {return(paste("Item", v))}))
# 
# g <- (ggplot(heatMapForPlot, aes(x = mouseX, y = mouseY, color = condition)) +
#       geom_vline(xintercept = c(0, 150,300,450, 600)) +
#       geom_hline(yintercept = c(0, 150,300,450, 600)) +
#       geom_point() +
#       geom_point(aes(x = begTargetX, y = begTargetY), size = 20,
#                  shape = 4, color = "black", show_guide = FALSE) +
#       geom_point(aes(x = begDistrX, y = begDistrY), size = 20,
#                  shape = 4, color = "grey50", show_guide = FALSE) + 
#       theme(panel.grid.major = element_blank(), 
#             panel.grid.minor = element_blank()) +
#       xlim(0, 600) +
#       ylim(0, 600) +
#       theme(aspect.ratio = 1) +
#       facet_wrap(~ new_labels, nrow = 2))
# g
```

>>>>

setwd('~/Repos/keysar_replication/experiment2/data/')
preMouseDExp2 = read.csv('mouse/exp2Mouse.csv')
preErrorDExp2 = read.csv('error/exp2Error.csv')
preMessageDExp2 = read.csv('message/exp2Message.csv')
library(tidyr)
library(dplyr)
library(ggplot2)
library(lme4)
library(lmerTest)

d <- d.b %>%
  mutate(trait = sentence %in% c('Decisive', 'Competitive', 'Self-reliant', 
                                 'Willing to take risks' , 'Ambitious', 'Daring' , 
                                 'Adventurous' , 'Courageous')) %>%
  mutate(traitType = factor(ifelse(trait == TRUE, "Masculine", "Feminine"))) %>%

@@

```{r}
itemInequalitiesExp1 <- errorDExp1 %>%
  filter(condition == "exp") %>%
  filter(criticalError == 1) %>%
  filter(attemptNum == 0) %>%
  group_by(objectSet) %>%
  tally() %>%
  right_join(numPlayersPerConditionExp1, by = c('objectSet')) %>%
  mutate(objectSet = objectSet,
         errorCount = n, 
         correctCount = total - n) %>%
  mutate(errorRate = errorCount / (errorCount + correctCount)) %>%
  select(objectSet, errorCount, correctCount, errorRate, total)
itemInequalitiesExp1[1,2:4] = c(0, itemInequalitiesExp1[1,]$total, 0)

itemInequalitiesExp2 <- errorDExp2 %>%
  filter(condition == "exp") %>%
  filter(criticalError == 1) %>%
  filter(attemptNum == 0) %>%
  group_by(objectSet) %>%
  tally() %>%
  right_join(numPlayersPerConditionExp2, by = c('objectSet')) %>%
  mutate(objectSet = objectSet,
         errorCount = n, 
         correctCount = total - n) %>%
  mutate(errorRate = errorCount / (errorCount + correctCount)) %>%
  select(objectSet, errorCount, correctCount, errorRate, total)

@@

```{r}
library(binom)

Exp1Errs = itemInequalitiesExp1 %>%
  mutate(response = errorRate) %>%
  mutate(measure = "error") %>%
  do(mutate(., lower = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$lower,
               upper = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$upper)) %>%
  select(objectSet, response, measure, lower, upper)

@@

Exp1ItemwiseForPlot = rbind(Exp1PlottingDF, Exp1Errs)

g <- (ggplot(Exp1ItemwiseForPlot, aes(x = objectSet, y = response, 
                                      group = measure, fill = measure))
  + geom_bar(stat = "identity", position = "dodge")
  + geom_errorbar(aes(ymax = upper, ymin = lower), 
                  position = dodge, width = 0.25)
  + theme_bw(base_size = 16) 
  + ggtitle("Exp.1 Item-Wise Error")
  + ylab("ratio (scaled)"))
g
ggsave("../../writing/cogsci-submission/images/itemWiseFitness.pdf")
```

@@

```{r}
mouDataExp1 <- mouseDExp1 %>%
  filter(attemptNum == 0)

mDExp1 <- messageDExp1 %>% 
  filter(attemptNum == 0) %>%
  filter(sender == "director") %>%
  group_by(gameid, objectSet, instructionNum) %>%
  mutate(messageStamp = first(time)) %>%
  select(gameid, condition, attemptNum, instructionNum, critical, 
         objectSet,sender,contents,messageStamp) %>%
  distinct(gameid,contents)

joinedExp1 <- mouDataExp1 %>% 
  right_join(mDExp1, by = c("gameid", "condition", "objectSet", 
                             "instructionNum", "attemptNum", "critical"))

mouDataExp2 <- mouseDExp2 %>%
  filter(attemptNum == 0)

@@

joinedExp2 <- mouDataExp2 %>%
  left_join(mDExp2, by = c("gameid", "condition", "objectSet", "attemptNum",
                               "instructionNum", "critical")) #%>%
```

```{r}
dExp1 <- joinedExp1 %>% 
  filter(critical == 1) %>% 
  group_by(objectSet, condition) %>%
  filter(time > messageStamp) %>%
  mutate(mouseY = 600 - mouseY) %>%
  mutate(targetY = 600 - targetY) %>%
  mutate(begTargetX = first(targetX),
         begTargetY = first(targetY)) %>%
  filter(targetX == begTargetX) %>%
  filter(targetY == begTargetY) %>%
  select(gameid, time, messageStamp, condition, 
         objectSet, instructionNum, targetX, targetY, mouseX, mouseY) %>%
  mutate(experiment = "Exp.1")

dExp2 <- joinedExp2 %>% 
  filter(critical == 1) %>% 
  group_by(objectSet, condition) %>%
  filter(time > messageStamp) %>%
  mutate(mouseY = 600 - mouseY) %>%
  mutate(targetY = 600 - targetY) %>%
  mutate(begTargetX = first(targetX),
         begTargetY = first(targetY)) %>%
   filter(targetX == begTargetX) %>%
   filter(targetY == begTargetY) %>%
  select(gameid, time, messageStamp, condition, 
         objectSet, instructionNum, targetX, targetY, mouseX, mouseY) %>%
  mutate(experiment = "Exp.2")
```

@@

intermediateHeatMap <- rbind(dExp1, dExp2) %>%
  group_by(gameid, objectSet, condition, experiment) %>%
  mutate(inTargetSquare = as.numeric(mouseX > targetX - 75 
                                     & mouseX < targetX + 75
                                     & mouseY > targetY - 75
                                     & mouseY < targetY + 75)) %>%
  filter(inTargetSquare == 1) %>%
  summarise(messageTime = mean(messageStamp),
            startTimeInTarget = first(time),
            endTime = last(time))

combinedHeatMap = intermediateHeatMap %>%
    group_by(gameid, condition, experiment) %>%
    summarise(targetHoverPercentage = mean((endTime - startTimeInTarget)/ 
                                           (endTime - messageTime)))
View(combinedHeatMap)

# Easier to report these as paired t-tests
percentExp1 <- lmer(targetHoverPercentage ~ condition + (1 | gameid), 
           data = combinedHeatMap %>% filter(experiment == "Exp.1"))
summary(percentExp1)
percentExp2 <- lmer(targetHoverPercentage ~ condition + (1 | gameid), 
           data = heatMapForLMExp2 %>% filter(experiment == "Exp.2"))
summary(percentExp2)
percentExpVs <- lmer(targetHoverPercentage ~ condition * experiment + (1 | gameid),
                     data = combinedHeatMap)
summary(percentExpVs)
```

@@

```{r}
stat = function(data, indices) {
  d <- data[indices,]
  output = d %>%
    group_by(condition, experiment) %>%
    summarise(targetHoverPercentage = mean((endTime - startTimeInTarget)/ 
                                           (endTime - messageTime)))
  return(output$targetHoverPercentage)
}

heatMapBoot = boot(data = intermediateHeatMap, statistic = stat, R = 1000)
Exp1baseCI = boot.ci(heatMapBoot, type = "basic", index=1)
Exp2baseCI = boot.ci(heatMapBoot, type = "basic", index=2)
Exp1expCI = boot.ci(heatMapBoot, type = "basic", index=3)
Exp2expCI = boot.ci(heatMapBoot, type = "basic", index=4)

plottingDF = data.frame(condition = c("base", "base", "exp", "exp"),
                        experiment = c("Exp.1", "Exp.2", "Exp.1", "Exp.2"),
                        response = heatMapBoot$t0,
                        lowerCI = c(Exp1baseCI$basic[1,4], Exp2baseCI$basic[1,4],
                                    Exp1expCI$basic[1,4], Exp2expCI$basic[1,4]),
                        upperCI = c(Exp1baseCI$basic[1,5], Exp2baseCI$basic[1,5],
                                    Exp1expCI$basic[1,5], Exp2expCI$basic[1,5]))

# heatMapForPlot = combinedHeatMap %>% 
#   group_by(condition, experiment) %>%
#   summarize(error = ci95(targetHoverPercentage),
#             percent = mean(targetHoverPercentage))

g <- (ggplot(plottingDF, aes(x = experiment, y = response, 
                                  group = condition, fill = condition)) 
      + geom_bar(position = dodge, stat= "identity")
      + geom_errorbar(aes(ymax = upperCI, 
                          ymin = lowerCI), position = dodge,
                          width = 0.25)
      + ylim(0, .4)
      + theme_bw(base_size = 16)
      + ylab("% of total decision window")
      + ggtitle("Target Hover-Time"))
g
ggsave("../../writing/cogsci-submission/images/mousetracking.pdf")
```
